\chapter{Introduction}\label{chapter:introduction}

\input{chapters/introduction/setting}

\section{Motivation}
\subsection{Superlight Clients}

\todo{continuity}

Given an honestly adopted chain, consensus security is based on the premise that
it is difficult to create a competing chain which deviates significantly and has
more proof-of-work than the existing honestly adopted chain. To determine which
financial history is the valid one, a \emph{verifier} node connected anew to the
network must download.

 convince a node
that a chain is the longest one, the proof-of-work of every block in the chain
must be presented and verified. This chain $\chain$ grows linearly with time.
The first problem we concern ourselves with

\todo{continuity}

Proof-of-work blockchain clients such as mobile wallets today are based on the
Simplified Payment Verifications (SPV) protocol, which was described in the
original Bitcoin paper~\cite{bitcoin}, and allows them to sychronize with the
network by downloading only block headers and not the entire blockchain with
transactions. However, such initial synchronization still requires receiving all
the block headers. In this work, we study the question of whether better
protocols exist and in particular if downloading fewer block headers is
sufficient to securely synchronize with the rest of the blockchain network. Our
requirement is that the system remains decentralized and that useful facts about
the blockchain (such as the Merkle root of current account balances in
Ethereum~\cite{wood,buterin}) can be deduced from the downloaded data.

\subsection{Interoperability}
Since the invention of Bitcoin in 2009, numerous other cryptocurrencies have
followed, improving upon Bitcoin on several aspects. The most prolific of these
is \emph{Ethereum}~\cite{buterin}, which introduces the concept of \emph{smart
contracts}. These Turing-complete programs enable developers to define complex
conditions which must be satisfied to spend money, beyond the simple signatures
that Bitcoin allows as conditions for spending. They are programmed in
specialized programming languages such as Solidity and run on top of the
Ethereum Virtual Machine~\cite{wood}. Each contract is a sovereign entity that
can own money and define the rules under which this money can be spent. These
contracts execute autonomously. Their correct execution is verified by miners on
the network, in a similar way that signatures are verified in Bitcoin's case.

Other cryptocurrencies that include significant contributions and
experimentation are \emph{Litecoin}~\cite{litecoin} which aims to be more
egalitarian~\cite{egalitarianism}; \emph{Monero}~\cite{cryptonote} and
\emph{ZCash}~\cite{zerocoin,zcash}, which improve upon the generally
poor~\cite{fistful,quantitative-bitcoin-analysis,tumblebit} privacy of
Bitcoin; \emph{Namecoin}~\cite{namecoin} which was a first attempt at creating a
decentralized DNS alternative; \emph{Dogecoin}~\cite{dogecoin}, which experiments with
inflationary economics in contrast to Bitcoin's deflationary nature;
\emph{Bitcoin Cash}~\cite{btcVSbch}, which experiments with larger block sizes; and
\emph{Cardano}~\cite{ouroboros}, which uses proof-of-stake instead of proof-of-work.

It is possible to \emph{trade} one coin for the other. For example, if one
wishes to exchange Bitcoin for Ethereum, they need to find a counterparty who
wishes to exchange Ethereum for Bitcoin (this is generally easy to do through
centralized services). However, each of these blockchain systems remains
isolated. The concept of a \emph{cryptocurrency} and its respective \emph{chain}
remains intertwined: A Bitcoin lives in the Bitcoin chain, while an Ether lives
in the Ethereum chain. The \emph{interoperability} problem pertains to the
ability to move a cryptocurrency from its native chain to a remote chain,
a one-way peg\index{One-way Peg}, and then back, a two-way
peg\index{Two-way Peg}. If Bitcoin and Ethereum were interoperating, it would be
possible to move one Bitcoin from the Bitcoin chain to the Ethereum chain and
back. In a properly interoperating system, the Bitcoin would retain its nature
during its lifespan within the Ethereum chain. For example, it would maintain
the same exchange rate against other currencies as a Bitcoin living in the
Bitcoin chain. While on the Ethereum chain, it would also enjoy the benefits of
the Ethereum ecosystem. For example, it would make itself subject to smart
contracts.

\section{Our Contributions}
\subsection{Superblocks}

\todo{superblocks}
\todo{NIPoPoWs}
\todo{applications to superlight wallets}
\todo{applications to sidechains}
\todo{applications to logspace mining}
\todo{the variable difficulty and $\Delta$-delay setting}
\todo{proofs of stake}
\todo{application: superlight clients}
\todo{application: sidechains}
\todo{application: logspace mining}

\section{Related Work}
% KLS
% other sidechains works
% - omniledger
% - rootstock
% - Todd sidechains
% - xclaim
% - rootstock
% - polkadot
% - truebit?
% - flyclient
