\section{Blinded mining}

The protocol presented in the previous section is secure against
$\frac{1}{3}$-bounded adversaries. We note that the reason why an adversary with more
mining power is able to attack the scheme is because they are able to see which
blocks are $Q$-blocks so that they can selectively supress them. This motivates
us to design a protocol in which the $Q$-blockness of a block is not known to
the adversary until the block has been stabilized by being buried under $k$
subsequent blocks and can no longer be supressed. Therefore, we wish to keep
the superblock status secret for a duration of $k$ blocks.

We modify the honest protocol to work as follows. The \textsf{pow} function
works as usual and accepts as input the usual parameters $x$ (the transaction
data) and $s$ (the reference to the previous block) and finds a $ctr$ such that
$H(ctr || x || s) \leq T$. The honest party broadcasts $x$ and $s$, but keeps
$ctr$ private. It then generates a commitment $s' = \textsc{Com}(H(ctr || x ||
s))$ which commits to the block hash $H(ctr || x || s)$. Next, it generates a
zero knowledge proof $\pi$ proving the following statement: I know an $ctr$ such
that $s'$ commits to $H(ctr || x || s)$  and $H(ctr || x || s) \leq T$. The
commitment and the zero-knowledge proof are then broadcast by the party.

Mining is performed by setting the first $s$ to be a predefined string (genesis)
as usual. Each next miner then builds on top of $s'$, the commitment to the
previous block, instead of building on top of the usual $H(ctr || x || s)$. As
the new block points to the commitment, this is sufficient commitment to ensure
proof-of-work security.

The value $ctr$ is kept secret by the generating party until the newly generated
block is buried under subsequent $2k$ blocks according to the view of the party
which originally generated the block. At that point, the party reveals $ctr$
through a revealing transaction $\text{tx}_\text{reveal}$ which includes the
$ctr$ value as well as the commitment opening for $s'$ showing that the
particular $ctr$ value is the one that was committed to. This transaction is
included by an honest miner as long as the chain does not contain a previous
commitment opening for that particular block.

To incentivize this honest behavior, we mandate that the miners are paid only
\emph{after} opening their commitment. However, if a commitment opening is done
prior to $k$ blocks after the commitment is placed in a block, the rewards are
slashed and the miner is not paid. For more details, see
Section~\ref{sec.deploy}.

\import{./}{chapters/superlight/trapdoor}
