\section{Block Suppression}

We begin our analysis by developing a probabilistic framework to
study whether the adversary can \emph{suppress} blocks of her
choice. The central definition here is the notion of a $Q$-block,
a block that possesses a certain property --- such as being a
$\mu$-superblock for some $\mu \in \mathbb{N}$. The main theorem
we will eventually prove is a generalization of the Common Prefix
property: That the Common Prefix property holds for blocks filtered
by any attribute $Q$. This will allow us to prove our protocol
is secure by instantiating $Q$-blocks as $\mu$-superblocks.

\import{./}{chapters/superlight/backbone.tex}

% $Q$-blocks <<<
We define a $Q$-block as a block satisfying a predicate $Q$ on its hash.
Note that this evaluation does not depend on any particular execution.

\begin{definition}[$Q$-block]
	A \emph{block property} is a predicate $Q$ defined on a hash output
	$h \in \{0, 1\}^\kappa$.
	Given a block property $Q$, a valid block with hash $h$ is called
	a $Q$-block if $Q(h)$ is true.
\end{definition}

The block properties we are interested in will be evaluated as
$Q(H(\left<ctr, s, x\right>))$
in actual
executions for particular blocks. As
such, we will be interested in properties which are polynomially
computable given $h$ as the input.

%>>>

% RANDOM VARIABLES <<<
\noindent
\textbf{Definitions of random variables.}

Recall a query of a party is \emph{successful} if it submits a triple
$(ctr,s,x)$ such that $H(ctr,s,x)\leq T$.
Let us generalize these definitions for block properties.
Consider a block property $Q$. Let $\xi_Q=\Pr[Q(h)|h\leq T]$, when $h$ is
uniformly distributed over the range of the hash function.
For each round $i$, query $j\in[q]$, and $k\in[t]$ (the $k^\text{th}$ party
controlled by the adversary), we define Boolean random
variables $X_Q(i),Y_Q(i)$ and $Z_Q(i,j,k)$ as follows.
If at round $i$ an honest party obtains a $Q$-block, then $X_Q(i)=1$,
otherwise $X_Q(i)=0$.
If at round $i$ exactly one honest party obtains a $Q$-block, then
$Y_Q(i)=1$, otherwise $Y_Q(i)=0$.
Regarding the adversary, if at round $i$, the $j^\text{th}$ query of the $k^\text{th}$
corrupted party obtains a $Q$-block, then $Z_Q(i,j,k)=1$, otherwise
$Z_Q(i,j,k)=0$.
Define also $Z_Q(i)=\sum_{k=1}^t\sum_{j=1}^qZ_Q(i,j,k)$.
For a set of rounds $S$, let $X_Q(S)=\sum_{r\in S}X_Q(r)$ and similarly
define $Y_Q(S)$ and $Z_Q(S)$.
We drop the subscript from all variables $X,Y,Z$, when the $Q$-block is
simply the property of being a valid block.
Further, if $X(i)=1$, we call $i$ a \emph{successful round} and if
$Y(i)=1$, a \emph{uniquely successful round}.
%>>>

% BOUNDS ON EXPECTATIONS <<<
As in the backbone model, the probability $f$ that at least one honest party
computes a solution at given round is an important parameter.
Writing $p=T/2^\kappa$ for the probability of success of a single query, we
have
\[
	(1-f){pq(n-t)}\leq f=\Ex[X(i)]=1-(1-p)^{q(n-t)}\leq pq(n-t)
.\]
The following bounds relate the expectations of the random variables defined
above to $f$, for all $i$ and block properties $Q$.
\begin{gather*}
	\xi_Q f\leq\Ex[X_Q(i)]\leq\frac{\xi_Q f}{1-f},\quad
		\xi_Q f(1-f)<\Ex[Y_Q(i)],\\
	\Ex[Z_Q(i)]\leq\frac{\xi_Q f}{1-f}\cdot\frac t{n-t}
.\end{gather*}
For the derivations of these inequalities see Garay et al.~\cite{backbone-new}.
%>>>

\noindent
\textbf{Typical executions.}
We now define our typical set of executions, extending the typical executions
defined in Chapter~\ref{chapter:background}.
This follows the backbone model, but
extended to include block properties.
Informally, this set consists of
those executions with polynomially many rounds and with the property that all
the random variables of interest over sufficiently many (at least
$\lambda=\Omega(\kappa)$) consecutive rounds do not deviate too much from
their expectation.
To this end, recall the following terms. An
\emph{insertion} occurs when, given a chain $\chain$ with two consecutive
blocks $B$ and $B'$, a block $B^*$ created after $B'$ is such that $B,B^*,B'$
form three consecutive blocks of a valid chain. A \emph{copy} occurs if the
same block exists in two different positions. A \emph{prediction} occurs when
a block extends one which was computed at a later round.

\begin{definition}[Typical execution]\label{def:typical}
	For a real $\eps\in(f,\frac14)$, integer $\lambda$, and
	a collection of polynomially many block properties $\mathcal{Q}$, we say an
	execution is $\mathcal{Q}$-\emph{typical} (or simply typical), if the following
	hold.
	\begin{itemize}
		\item
			For any $Q\in\mathcal{Q}$ and any set $S$ of at least $\lambda/\xi_Q$
			consecutive rounds we have
			\begin{align}
				(1-\eps)\Ex[X_Q(S)]<~&X_Q(S)<(1+\eps)\Ex[X_Q(S)],
				\\(1-\eps)\Ex[Y_Q(S)]<~&Y_Q(S),
				\\&Z_Q(S)<\Ex[Z_Q(S)]+\eps\Ex[Y_Q(S)].
			\end{align}
		%\item
		%	For any $\D,i\in[L]$ and $Q\in\mathcal{Q}$, if
		%	$\sum_{j\geq i}A_\D(j)Z_Q(j)\geq k$, then
		%	\begin{equation}
		%		\sum_{j\geq i}A_\D(j)Z_Q(j)\leq(1+\eps)\xi_Q\sum_{j\geq i}A_\D(j)
		%	.\end{equation}
		\item
			No insertions, no copies, and no predictions occurred.
	\end{itemize}
\end{definition}%>>>

\begin{theorem}\label{theorem:alltypical}%<<<
	If $t<(1-\delta)(n-t)$ with $\delta>3\eps+3f$,
	an execution is typical with probability $1-e^{-\Omega(\eps^2f\lambda)}$.
\end{theorem}
\begin{proof}
	The proof uses standard Chernoff bounds, along the lines of \cite{backbone-new}.
	We just note that the variables $X_Q(i)$ (and similarly $Y_Q(i)$ and
	$Z_Q(i,j,k))$ are independent Bernoulli trials for each $Q$ and successful
	with probability $\Theta(\xi_Qf)$. In addition, a union bound is applied
	over all $Q$.
\end{proof}%>>>

\begin{lemma}\label{lemma:typical}%<<<
	Assume $t<(1-\delta)(n-t)$ with $\delta>3\eps+3f$ and a $\mathcal{Q}$-typical
	execution.
	Then, the following hold for any $Q\in\mathcal{Q}$ and any set $S$ of at least
	$\lambda/\xi_Q$ consecutive rounds.
	\begin{itemize}
	\item[(a)]
		$(1-\eps)\xi_Qf|S|<X_Q(S)<(1+\eps)\cdot\frac{\xi_Qf}{1-f}\cdot|S|$.
	\item[(b)]
			$(1-\frac\delta3)\xi_Qf|S|<(1-\eps)\xi_Qf(1-f)|S|<Y_Q(S)$.
	\item[(c)]
		$Z_Q(S)<(\frac t{n-t}\cdot\frac1{1-f}+\eps)\cdot\xi_Qf|S|
			\leq(1-\frac{2\delta}3)\xi_Qf|S|$.
	%\item[(d)]
	%	$Z_Q(S)
	%		<(1+\frac\delta2)\cdot\frac t{n-t}\cdot X_Q(S)+\frac{\eps f}{1-f}\cdot|S|
	%		%<(1+\frac\delta2)\cdot\frac t{n-t}\cdot X(S)+\eps f|S|
	%		<(1-\frac\delta3)X(S)$.
	\item[(e)] $Z_Q(S)<Y_Q(S)$.
	\end{itemize}
\end{lemma}
\begin{proof}
	This follows with straightforward calculations from the properties of
	a typical execution, the bounds
	on the expectations of the involved random variables, and the assumed bounds
	on $t/n,\delta,\eps$ and $f$.
\end{proof}
%>>>

We now establish an upper bound in the number of
$Q$-blocks an adversary can suppress, regardless of what attack method she
follows.

% PAIRING LEMMA <<<
Uniquely successful rounds have the following important property~\cite{backbone-new}.
\begin{lemma}[Pairing]\label{lemma:pairing}
	For any $i$ and any pair of distinct blocks $\chain[i]$ and
	$\chain'[i]$, if $\chain[i]$ was computed by an honest party in a uniquely
	successful round, then $\chain'[i]$ was computed by the adversary.
\end{lemma}
\begin{proof}
	Let $r$ be the uniquely successful round that $\chain[i]$ was computed.
	No honest party would extend $\chain'[i-1]$ at a round later than $r$, since
	every honest party would have a chain of length at least $i$.
	Similarly, if an honest party computed $\chain'[i]$ at some round
	earlier than $r$, then no honest party would have extended $\chain[i-1]$ at
	round $r$.
	Finally, $\chain'[i]$ cannot have been computed by an honest party at round
	$r$, since $r$ was a uniquely successful round.
\end{proof}
%>>>

% INTERVAL-COVER LEMMA <<<
\begin{lemma}[Suppression]\label{lemma:balanced}
	If $r$ is a uniquely successful round and the corresponding block
	does not belong to the chain of an honest party at a later round,
	then there is a set of consecutive rounds $S$ such that
	$r\in S$ and $Y(S)\leq Z(S)$.
\end{lemma}
\begin{proof}
	Let $\chain$ be the chain of the honest party that was successful at round
	$r$ and $u$ the depth of the corresponding block.
	Let $r'$ be the first round after $r$ in which an honest party has a chain
	$\chain'$ which does not contain block $\chain[u]$. Let $\chain'[u']$ the
	last block of $\chain'$ at round $r'$.
	Let $\chain[u^*]=\chain'[u^*]$ be the last honest block on the common prefix
	of $\chain$ and $\chain'$, and let $r^*$ be its timestamp.
	We claim that the set $S=\{i:r^*<i<r'\}$ satisfies the requirements of the
	statement.
	Clearly, $r\in S$. Let us verify that $Y(S)\leq Z(S)$.
	Indeed, if $\chain^*[v]$ is any block computed during a uniquely successful
	round $i\in S$, it must hold $u^*<v\leq u'$. The first inequality is because
	the party computing $\chain^*[v]$ knows of $\chain[u^*]$ (it was announced
	at round $r^*$ and received by round $i>r^*$) and would not mine on
	a shorter chain.
	The second inequality holds because $v>u'$ contradicts an honest party
	having a chain of length $u'$ at round $r'>i$ (since $\chain^*[v]$ was
	received by round $r'$).
	The inequality then follows by Lemma~\ref{lemma:pairing}, since it is always
	possible to find a block distinct from $\chain^*[v]$ on $\chain$ or
	$\chain'$ (we may use $\chain'$, unless $\chain^*[v]$ is on $\chain'$, in
	which case---due to the minimality of $r'$---we have $v<u$ and we can use
	$\chain$).
\end{proof}

An observation that follows from the above lemma is that if
the adversary manages to suppress a $Q$-block from the chain of an honest party
and this $Q$-block was computed in a uniquely successful round,
then we can associate with it an adversarial block.
In particular, if $r$ is a uniquely successful round and the corresponding
block does not belong to the chain of an honest party at a later round, then
there is an \emph{associated} adversarial block of the same height that was
adopted by an honest party.
% >>>

% Unsuppressibility Lemma <<<
We now state and prove our Unsuppressibility Lemma. Informally, the lemma says that if the
number of blocks the adversary obtained in a set of consecutive rounds is $z$
and the number of the uniquely successful blocks the honest parties obtained
in the same set of rounds is $y$, then there exist $y-2z$ blocks that will
always belong to the chain of every honest party.
It follows that if the power of the adversary is bounded below 1/3 of the
total power, then with overwhelming probability there will be a nonzero number of such
blocks.

An important note with respect to the Unsuppressibility Lemma is the following.
Fix all the randomness the random oracle requires for a given execution.
This determines the successful queries of every party and therefore determines
the parameters $y$ and $z$ above. The observation is that even if these
random coins are revealed to the adversary at the beginning of the execution,
one can determine precisely which $y-2z$ blocks ---and no matter the
adversary's strategy--- will always belong to the chain of every honest party.

\begin{lemma}[Unsuppressibility]\label{lem:unsuppressibility}
	In a typical execution,
	every set of consecutive rounds $U$ has a subset\/ $S$ of uniquely
	successful rounds, such that
	\begin{itemize}
		\item
			$|S|\geq Y(U)-2Z(U)-2\lambda f(\frac t{n-t}\cdot\frac1{1-f}+\eps)$ and
		\item
			after the last round in $S$ the blocks corresponding to\/ $S$ belong to
			the chain of every honest party.
	\end{itemize}
\end{lemma}
\begin{proof}
	Let $U'$ be the set of consecutive rounds that contains $U$ and also the
	$\lambda$ rounds that come before and after $U$.
	By Lemma~\ref{lemma:balanced}, we may take $S$ to contain all those uniquely
	successful rounds $r\in U$ such that for any set of consecutive rounds
	$S'\subseteq U'$ containing $r$, $Y(S')>Z(S')$. Note that, in a typical execution,
	no such $S'$ may contain elements outside $U'$.
	Letting $y=Y(U)$ and $z=Z(U)$, we
	need to show $y-|S|\leq 2z+2(1-\frac{2\delta}{3})\lambda f$.

	Let us focus on the uniquely successful rounds not in $S$.
	%; call this set of rounds $\bar S$.
	Consider a collection $\mathcal{T}$ of sets of consecutive rounds with the
	following properties.
	\begin{itemize}
		\item
			For all $T\in\mathcal{T}$, $Y(T)\leq Z(T)$.
		\item
			For each $r\in U\setminus S$, there is a $T\in\mathcal{T}$ that contains $r$.
		\item
			$|\mathcal{T}|$ is minimum among all collections with the above properties.
	\end{itemize}
	We now observe that the minimality condition on $\mathcal{T}$ implies that no round
	$r$ with $Z_r>0$ belongs to more than two sets of $\mathcal{T}$. If that was the
	case, then there would be three sets $T_1,T_2,T_3$ in $\mathcal{T}$ with
	$T_1\cap T_2\cap T_3\neq\emptyset$. But then, we could keep the two sets
	with the leftmost and rightmost endpoints, contradicting the minimality of
	$\mathcal{T}$. Furthermore, no round in $U'\setminus U$ belongs to more than one set
	of $\mathcal{T}$. Thus,
	\[
		y-|S|=\sum_{i\in U\setminus S}Y_i
			\leq\sum_{T\in\mathcal{T}}Y(T)
			\leq\sum_{T\in\mathcal{T}}Z(T)
			\leq 2z+Z(U'\setminus U)
			%\leq 2z+\frac{2\lambda f}{1-f}\Bigl(\frac t{n-t}+\eps\Bigr)
			%\leq 2z+2(1-\frac{2\delta}{3})\lambda f
	.\]
	The third inequality holds because every round in which the adversary
	was successful is counted at most twice inside $U$ and at most once outside
	$U$ (by the discussion above the inequalities). Finally,
	using $|U'\setminus U|\leq 2\lambda$ and Lemma~\ref{lemma:typical}(c) we
	obtain the stated bound.
\end{proof}

%\nikos{Sketch strategy and argument of optimality.}

%\nikos{Do we want a formal statement about optimality?}

The proof of this lemma is quite generous to the adversary on two
accounts. First, it reveals to the adversary all coin flips in the beginning
of the execution. Second, it gives the adversary two choices for each one of
his blocks, and assumes that he will be able to choose among these as he sees
fit. Nevertheless, we conjecture that the bound $y-2z$ cannot be substantially
increased in the case the property is rare.

%\nikos{Requiring $t<(\frac12-\delta)(n-t)$ and $2f+2\eps\leq\delta$ gives that
%for any set $S$ of consecutive rounds in a typical execution
%$
%	Y(S)-2Z(S)>\delta(1-\eps)(1-f)f|S|>\frac\delta2\cdot f|S|
%.$}
%>>>

% COROLLARIES<<<
%\nikos{The next two don't contain the error term. Need to be fixed if we want
%them.}
%
%\begin{corollary}
%	Let\/ $S$ be the set of rounds of an execution. If\/ $Y(S)>3Z(S)$, then
%	there are more than\/ $\frac13\cdot Y(S)$ honest blocks in the chain of
%	every honest party.
%\end{corollary}
%\begin{proof}
%	By Lemma~\ref{lemma:balanced}, the chain of every honest party has at least
%	$Y(S)-2Z(S)>Y(S)-\frac23\cdot Z(S)\geq\frac13\cdot Y(S)$ honest blocks.
%\end{proof}
%\begin{corollary}
%	Assuming\/ $t<(\frac14-\delta)n$ and a typical execution, any honest chain
%	has more honest $Q$-blocks than the total number of adversarial ones.
%\end{corollary}
%\begin{proof}
%	Let $Y$ denote the total number of uniquely successful rounds in the
%	execution and $Z$ the total number of adversarial blocks computed.
%	In a typical execution, $Y>3Z$. By the corollary, there are more than $Z$
%	honest blocks in the chain of every honest party.
%\end{proof}
%>>>

We can now prove that an adversary with less than $1/3$ of the total mining power
cannot create a chain with more $Q$-blocks than an honest chain. Such a task
would require the adversary to both suppress many $Q$-blocks from the honest
chain \emph{and} to obtain many of them for the adversarial chain.

\begin{lemma}[$Q$-block Common-Prefix]\label{lemma:qblockcommonprefix}
	Assume $t<(\frac13-\delta)n$ with $\delta>3\eps+3f$ and a $\mathcal{Q}$-typical
	execution.
	Consider a round at which a chain $\chain$ is adopted by an honest party and
	suppose there exist another chain $\chain'$ such that
	$\chain'\setminus(\chain'\cap\chain)$ has at least $22\lambda\xi_Qf$ $Q$-blocks.
	Then, with overwhelming probability, $\chain$ has more $Q$-blocks than $\chain'$.
\end{lemma}
\begin{proof}
	Assume an execution in which the assumptions of the lemma hold.
	Let $r^*$ be the round on which the last honest block on
	$\chain^*=\chain\cap\chain'$ was computed (if no such block exists let
	$r^*=0$) and define the set of rounds $S=\{i:r^*<i\leq r\}$.
	%Let also $B$ denote the first block of $\chain'\setminus\chain^*$.
	%Let $r'>r^*$ be the round on which the $k$th block on
	%$\chain'\setminus(\chain'\cap\chain)$ was computed and define the set of
	%rounds $S=\{i:r'\leq i\leq r\}$.
	We will study the execution during the rounds in $S$.
	To that end, let $W'$ denote the set of adversarial queries
	on $\chain'\setminus\chain^*$ at some round at least $\lambda$ greater from
	$r^*$. Denote by $W$ the rest of the adversarial queries in $S$.

	We first observe that no query in $W'$ could have suppressed
	a $Q$-block on $\chain$.
	As in the proof of Lemma~\ref{lemma:balanced}, in such a case there would
	exist a set of consecutive rounds $|S^*|\geq\lambda$ such that $Y(S^*)\leq
	Z(S^*)$.
	This contradicts the last item of Lemma~\ref{lemma:typical}.

	From this observation and the Unsuppressibility Lemma, there are at least
	$Y(S)-2Z(W)-2\lambda f(\frac t{n-t}\cdot\frac1{1-f}+\eps)$
	blocks that the adversary cannot
	suppress.
	Each of these is a $Q$-block independently with probability $\xi_Q$.
	Under our assumptions,
	$2(\frac t{n-t}\cdot\frac1{1-f}+\eps)<\frac{1-\delta}{1-\eps}$.
	We conclude that, with overwhelming probability, there are at least
	\[
		(1-\eps)\xi_Q\cdot\bigl[Y(S)-2Z(W)\bigr]-(1-\eps)\lambda\xi_Qf
	\]
	$Q$-blocks on $\chain\setminus\chain^*$.

	On the other hand, the number of $Q$-blocks on $\chain'\setminus\chain^*$ is
	at most the $Q$-blocks from the $W'$ queries plus the $Q$-blocks
	from the initial $\lambda$ rounds.
	The latter can be shown to be at most $3\lambda\xi_Qf$.
	For the former, using Lemma~\ref{lemma:negbin} (with
	$F_j=1$ when $j\in W'$ and $M_j=1$ when it resulted in a $Q$-block) and
	Lemma~\ref{lemma:typical}, in a typical execution, are at most
	$(1+\eps)\xi_QZ(W')$. Thus, there at most
	\[
		(1+\eps)\xi_Qp|W'|+3\lambda\xi_Qf
	.\]
	$Q$-blocks on $\chain'\setminus\chain^*$.
	Since these are at least $22\lambda\xi_Qf$, it can be shown that
	the difference between the last two displayed expressions is at least
	$(1-\eps)\xi_Q\cdot[Y(S)-2Z(S)]$. This is positive in a typical execution
	in which the power of the adversary is bounded below $\frac13-\delta$ the
	total power.
\end{proof}

In the above proof, we made use of the following lemma
pertaining to the distribution of products of random variables.
For completeness, we also include its proof here.

\begin{lemma}\label{lemma:negbin}%<<<
	For each $j\in\N$, let $F_j$ and $M_j$ be Boolean random variables
	such that $\Ex[M_j]=\zeta$ and $M_j$ is independent of $F_i$ for $i\leq j$ and
	independent of $M_i$ for $i\ne j$. For any $\eps\in(0,1)$,
	\[
		\Pr\bigg[
			\sum F_jM_j>(1+\eps)\zeta\sum F_j
			~\bigwedge~
			\sum F_jM_j\geq k
		\,\bigg]
		\leq e^{-\Omega(\eps^2k)}
	.\]
\end{lemma}
\begin{proof}
	Since $\sum_{n\geq k}e^{-\Omega(\eps^2n)}=e^{-\Omega(\eps^2k)}$, by the union
	bound it suffices to show that
	\begin{equation}\label{eq:unionbound}
		\Pr\bigg[
			(1+\eps)\zeta\sum F_j<k
			~\bigwedge~
			\sum F_jM_j=k
		\,\bigg]
		\leq e^{-\Omega(\eps^2k)}
	.\end{equation}
	In the summations below, let $\alpha$ range over words in $\{0,1\}^*$ and
	$\beta$ be any word in $\{0,1\}^\ell$ of weight $k$.
	For a fixed $\alpha$, define $J_\alpha=\{j\in\N:F_j=1\}$
	and $B=(M_j)_{j\in J_\alpha}$.
	Also, for $j\in\N$, let $E_j$ denote the event
	$\{(\forall i<j)(F_i=\alpha_i$ and $i\in J\Rightarrow M_i=\beta_i)\}$.
	Then,
	\begin{align*}
		\Pr&[B=\beta]=\sum_\alpha\Pr[B=\beta,A=\alpha]
		\\&=\sum_\alpha\prod_j\Pr[F_j=\alpha_j|E_j]\prod_{j\in J}\Pr[B_j=\beta_j|E_j,F_j=\alpha_j]
		\\&=\sum_\alpha\prod_j\Pr[F_j=\alpha_j|E_j,B=\beta]\prod_{j\in J}\Pr[M_j=\beta_j]
		\\&=\sum_\alpha\Pr[A=\alpha|B=\beta]\cdot\zeta^k(1-\zeta)^{\ell-k}
		\leq\zeta^k(1-\zeta)^{\ell-k}
	.\end{align*}
	Thus, letting $\beta$ range over all words in $\{0,1\}^*$ of length less
	than $\frac k{(1+\eps)\zeta}$ and weight $k$ ending with 1,
	the left-hand side of $(\ref{eq:unionbound})$ is equal to
	\[
		\sum_\beta\Pr[B=\beta]
			\leq\sum_{k\leq\ell<\frac k{(1+\eps)\zeta}}{\ell-1\choose k-1}\zeta^k(1-\zeta)^{\ell-k}
	.\]
	That is, the probability is at most that of a random
	variable following a negative binomial distribution with parameters
	$k$ (the number of successes) and $\zeta$ (the probability of success)
	is less than $\frac k{(1+\eps)\zeta}$. The bound follows from standard
	Chernoff bounds.
\end{proof}
%>>>

\section{Analysis}

We are now ready to prove the construction of Algorithms~\ref{alg.compress}
and~\ref{alg.nipopow-verifier-distill}
secure
and succinct. For security, we denote $\Pi$ the proof presented by the honest party
and $\Pi'$ the proof presented by the adversary (but these can be given to the verifier
algorithm in any order). We can safely assume that these proofs were both generated
at round $r$ (the adversary could have generated the proof earlier, but not later,
than the honest party). The honest proof $\Pi$ was generated based on some honest
underlying chain $\chain$ using Algorithm~\ref{alg.compress}. On the other hand,
we have no guarantees about how the adversarial proof $\Pi'$ was generated. It
may be based on some underlying chain mined according to protocol, or not. In any
case $\Pi'$ \emph{does} form a chain and its blocks must have been mined in order, as
the verifier ensures this. However, there may not exist intermediate blocks covering
the whole proof-of-work as desired.

Security mandates that the verifier chooses the honest proof, $\Pi$. However, it
is possible that the verifier also chooses the adversarial proof, $\Pi'$, without
raising any issue, \emph{as long as it extends the honest proof} at a fork point
no longer than $k$ from the tip. To see why this is fine, note that an adversary
can already do this at the full blockchain: According to the Common Prefix property,
she can fork at a block at most $k$ blocks deep from the honest blockchain's end
and have up to $k$ blocks following the fork point. In this case, if it happens
that the verifier has chosen $\Pi'$, we require that
$(\Pi' \cap \chain)[-1] \in \chain[-k{:}]$. This means that the adversarial
proof extends the honest chain at some fork point in $\chain[-k{:}]$. But
let us contemplate what this entails: It means that the portion
$\Pi'\{(\Pi' \cap \chain)[-1]{:}\}$ is just a valid $0$-level extension of the
honest chain. As such, requiring
$|\Pi'\{(\Pi' \cap \chain)[-1]{:}\}| \geq
	 |\chain\{(\Pi' \cap \chain)[-1]{:}\}|$
would produce a competitive adversarial chain that is \emph{longer} than the
honest chain and it would be perfectly acceptable to a full node
(and by the common prefix property, this difference cannot be larger than $k$
blocks long). We must clearly allow for this possibility --- but it is not
a problem, as this situation can occur in full node executions, too.
This property also holds trivially in case the honest proof is chosen.

\begin{theorem}[Security]\label{thm.miner.security}
	Consider an arbitrary $\frac{1}{3}$-bounded PPT adversary $\mathcal{A}$
	in a typical execution. Let $\Pi$ be a proof generated by an honest
	party at round $r$ using Algorithm~\ref{alg.compress} by passing his underlying chain $\chain$.
	Let $\Pi'$ be an arbitrary proof generated by the adversary at round $r$.
	Let $\Pi^*$ be the proof accepted by the verifier using
	Algorithm~\ref{alg.nipopow-verifier-distill}.
	Then
	$|\Pi^*\{(\Pi^* \cap \chain)[-1]{:}\}| \geq
	 |\chain\{(\Pi^* \cap \chain)[-1]{:}\}|$
	with overwhelming probability.
\end{theorem}
\begin{proof}
	Let $\chain' = \Pi'$.
	We need to show that, either $\Pi$ will be the proof accepted by the verifier,
	or $\Pi^*$ is a proof extending the honest chain that is longer at level $0$,
	as mandated by the theorem statement.

	Let us consider first the case that a $\mu$ of Algorithm~\ref{alg.nipopow-verifier-distill} as above exists.
	When $\mu=0$, the verifier determines the longer chain and always
	correctly accepts the corresponding proof. That is, the verifier will
	either choose $\Pi^* = \Pi$, or, in case $\Pi^* = \Pi'$, the verifier
	will choose the adversarial proof $\Pi'$ which contains a $\chi'$ that extends the honest
	chain's $\chi$ at level $0$ (up to $k$ blocks long) with a longer alternative.
	This is the only case in which $\Pi'$ can win. For the other cases, we will
	now argue that the adversary cannot win.

	Let us now focus on the case $0<\mu\leq\ell$.
	Note that, since $\mathcal{D}[\mu-1]\cap\mathcal{D}'[\mu-1]=\emptyset$
	(by the minimality of $\mu$), \emph{both}
	superchains must have at least $m$ blocks after their common block $b$.
	The $Q$-block Common-Prefix Lemma implies that $\Pi$ is accepted.

	Next, consider the case that no such $\mu$ exists.
	Clearly, $\ell\ne\ell'$ (otherwise $\mathcal{D}[\ell]\cap\mathcal{D}'[\ell']$ would
	contain the genesis block) and we need to argue that $\ell>\ell'$.
	Assume ---towards a contradiction--- that $\ell<\ell'$ and consider the
	statement of the $Q$-block Common-Prefix Lemma instantiated with blocks of
	level $\ell+1$ as the $Q$-blocks.
	Together with $\ell<\ell'$, it implies that $\chain'$ has fewer than $m$
	$Q$-blocks after the common block with $\chain$ (since $\chain$ has fewer
	$Q$-blocks than $\chain'$ in total, it must also have fewer on its fork;
	and they must necessary share a common block, since both must begin
	with genesis).
	But then, both $\chain$ and $\chain'$ have fewer than $m$ $Q$-blocks after
	their common block. Since $\mathcal{D}[\ell]\cap\mathcal{D}'[\ell]=\emptyset$
	by assumption, this cannot be the case.
\end{proof}

\begin{theorem}[Succinctness]\label{thm.succinct}
	In a typical execution with $t < (\frac{1}{3} - \delta)n$ with
	$3\epsilon + 3f < \delta < \frac{1}{3}$ and letting $m = \lambda$,
	an honest miner's state is in $O(m^2\log(r))$ at round $r$.
\end{theorem}
\begin{proof}
	As $t < (\frac{1}{3} - \delta)n$ with
	$3\epsilon + 3f < \delta < \frac{1}{3}$, therefore
	$c = \Ex[Y] - 2\Ex[Z] - 2\lambda f(\frac{t}{n-t}\frac{1}{1-f} + \epsilon)$ will be
	a positive constant and for sets of consecutive rounds $U$ with
	$|U| \geq \lambda$,
	we will have
	$Y(U) - 2Z(U) - 2\lambda f(\frac{t}{n-t}\frac{1}{1-f} + \epsilon) > (1 - \epsilon)c|U|$.

	Consider a state $\Pi$ generated by an honest prover and suppose for
	contradiction that $|\Pi| \in \omega(m\log(r))$, where $r$ indicates the
	current round number. From the security of the
	scheme, this state will correspond to some underlying chain $\chain$ such that
	$\Pi$ is the compression of $\chain$. Consider the variables
	$(\mathcal{D}, \chi) = \textsf{Dissolve}_{m,k}(\chain)$. As $|\chi| = k$ is
	constant, therefore $|\bigcup_{d \in \mathcal{D}} d| \in \omega(m\log(r))$.
  Let $\ell = |\mathcal{D}|$.	It holds that $\ell \in O(\log(|\chain|))$.
  Consequently, $\sum_{d \in \mathcal{D}} |d| \in \omega(m\log(r))$. Therefore
  there must exist some $\mu$ such that $|\mathcal{D}[\mu]| \in \Omega(\lambda^2)$.
	Consider the maximum such $\mu$.

	We distinguish two cases.

	Case 1: $\mu = \ell$. Then consider $\mathcal{D}[\ell]$.
	Let $u_0$ denote the round during which $\mathcal{D}[\ell][0]$ was generated
	and $u_1$ denote the round during which $\mathcal{D}[\ell][-1]$ was generated
	and consider the set $U$ of consecutive rounds from $u_0$ to $u_1$. As
	$\mathcal{D}[\ell]$ forms a chain, we have that
	$|U| \geq |\mathcal{D}[\ell]| > \lambda$. Applying the Unsuppressibility Lemma, we obtain
	that at least $|S| \geq c|U| = c|\mathcal{D}[\ell]| \in \Omega(\lambda)$
	rounds of $U$ must have been uniquely successful and belong to the chain of
	every honest party. Therefore $|\mathcal{D}[\ell]\upchain^{\ell+1}| \geq (1 - \epsilon)\frac{|S|}{2}$. By the definition of $\ell$ this is impossible.

	Case 2: $0 \leq \mu < \ell$. By maximality of $\mu$, we have
	$|\mathcal{D}[\mu + 1]| \in O(\lambda)$, but
	$|\mathcal{D}[\mu]| \in \Omega(\lambda^2)$.
	By the definition of
	$\mathcal{D}[\mu] = \chain[{:}-k]\upchain^\mu[-2m{:}] \cup
	\chain[{:}-k]\upchain^\mu\{\chain[{:}-k]\upchain^{\mu+1}[-m]{:}\}$, clearly
	$|\chain[{:}-k]\upchain^\mu[-2m{:}]| = 2m$ so necessarily
	$\chain[{:}-k]\upchain^\mu\{\mathcal{D}[\mu+1][-m]{:}\} \in \Omega(\lambda^2)$. Therefore there exist blocks $A$ and $B$
	in $\mathcal{D}[\mu+1]$ and $\mathcal{D}[\mu]$ such that
	$|\mathcal{D}[\mu + 1]\{A{:}Z\}| = 1$, but
	$|\mathcal{D}[\mu]\{A{:}Z\}| \in \omega(\lambda)$. Similarly to case
	1, consider the rounds $u_0$ and $u_1$ during which blocks $A$ and $Z$ were
	generated respectively and the set of consecutive rounds $U$ from $u_0$ to
	$u_1$ with $|U| \in \omega(\lambda)$. Using the Unsuppressibility Lemma, there
	must exist a set of uniquely successful rounds $|S| \geq c|U|$ whose blocks
	have been adopted by all honest parties and of which at
	least $(1 - \epsilon)\frac{|S|}{2} \geq 0$ will be of level $\mu + 1$.
	Therefore there must exist a block between $A$ and $Z$ in
	$\mathcal{D}[\mu + 1]$.

	Both cases are contradictions.
\end{proof}

The previous theorem allows us to make miners reject incoming state that is too
large (more than polylogarithmic) without processing them fully.

We note here that our analysis critically relies on the honest majority
assumption holding \emph{throughout} the execution. The reason why
our verifiers can maintain a valid chain is that, once
they receive a chain $\chain$ which is the longest, they inductively know that
$\chain[-k]$ must contain valid application data snapshot. Then, since they have all the last
$k$ blocks, they can validate the transactions $\delta$ on the
snapshot obtained before further mining on top of them.

Comparing this result to Theorem~\ref{thm:optimistic-succinctness} of Chapter~\ref{chapter:work},
we observe that here, for the first time, succinctness is proven against all adversaries,
and not just in the optimistic setting. The whole machinery of Q-blocks and suppression
attacks was required before we could complete such a proof. Using an identical approach,
the succinctness of charity NIPoPoWs (of Chapter~\ref{chapter:work}) can also be proven
succinct in all settings, against $1/3$ adversaries.
