\section{Security of Burn}\label{sec:analysis}

We now move on to the analysis of our scheme. As the scheme is deterministic,
its correctness is straightforward to show.

\begin{theorem}[Correctness]
  The proof-of-burn protocol $\Pi$ of Section~\ref{sec:construction} is \emph{correct}.
\end{theorem}
\begin{proof}
  Based on Algorithm~\ref{alg.construction-ro}, $\BurnVerify(1^\kappa, t, \GenBurnAddr(1^\kappa, t)) = \textsf{true}$ if and only if $\GenBurnAddr(1^\kappa, t) = \GenBurnAddr(1^\kappa, t)$, which always holds as $\GenBurnAddr$ is deterministic.
\end{proof}

We now state a simple lemma pertaining to the distribution of Random Oracle
outputs.

\begin{restatable}[Perturbation]{lem}{restateLemPerturbation}
  \label{lem.perturbation}
  Let $p(\kappa)$ be a polynomial and
  $F: \{0,1\}^\kappa \longrightarrow \{0,1\}^\kappa$ be a permutation.
  Consider the process which samples $p(\kappa)$ strings $s_1, s_2, \dots, s_{p(\kappa)}$ uniformly at random from the set $\{0, 1\}^\kappa$. The probability that there exists $i \neq j$ such that $s_i = F(s_j)$ is negligible in $\kappa$.
\end{restatable}

We will now apply the above lemma to show that our scheme is unspenable.

\begin{theorem}[Unspendability]
  If $H$ is a \emph{Random Oracle}, then the protocol $\Pi$ of Section~\ref{sec:construction} is \emph{unspendable}.
\end{theorem}
\begin{proof}
  Let $\mathcal{A}$ be an arbitrary probabilistic polynomial time $\spendattack$ adversary.
  $\mathcal{A}$ makes at most a polynomial number of queries $p(\kappa)$ to the Random Oracle.
  Let $\textsc{Match}$ denote the event
  that there exist $i \neq j$ with $s_i = F(s_j)$ where $F(s) = s \xor 1$.

  If the adversary is successful then it has presented $t, pk, pkh$ such that $H(pk) = pkh$ and $H(t) \xor 1 = pkh$.
  Observe that $\spendattack_{\mathcal{A}, \Pi}(\kappa) = \true \Rightarrow \textsc{Match}$.
  Therefore $\Pr[\spendattack_{\mathcal{A}, \Pi}(\kappa)] \leq Pr[\textsc{Match}]$. Apply Lemma~\ref{lem.perturbation} on $F$
  to obtain
  $\Pr[\spendattack_{\mathcal{A}, \Pi}(\kappa)] \leq \negl$.
\end{proof}

We note that the security of the signature scheme is not needed to prove unspendability. Were the signature scheme of the underlying cryptocurrency ever found to be \emph{forgeable}, the coins burned through our scheme would remain unspendable. We additionally remark that the
choice of the permutation $F(x) = x \xor 1$ is arbitrary. Any one-to-one
function beyond the identity function would work equally well.

\noindent
\textbf{Preventing proof-of-burn.}
It is possible for a cryptocurrency to prevent proof-of-burn by requiring every address to be accompanied by a proof of possession~\cite{pop}. To the best of our knowledge, no cryptocurrency features this.

Next, our binding theorem only requires that the hash function used is collision
resistant and is in the standard model.

\import{./}{chapters/sidechains/algorithms/alg.collision-adversary.tex}

\begin{theorem}[Binding]
  If $H$ is a \emph{collision resistant} hash function then the protocol of Section~\ref{sec:construction} is \emph{binding}.
\end{theorem}
\begin{proof}
  Let $\mathcal{A}$ be an arbitrary adversary against $\Pi$.
  We will construct the Collision Resistance adversary $\mathcal{A}^*$ against $H$.

  The collision resistance adversary, illustrated in Algorithm~\ref{alg.collision-adversary}, calls $\mathcal{A}$ and obtains two outputs, $t$ and $t'$. If $\mathcal{A}$ is successful then $t \neq t'$ and $H(t) \xor 1 = H(t') \xor 1$. Therefore $H(t) = H(t')$.

  We thus conclude that $\mathcal{A^*}$ is successful in the $\collisionattack$ game if and only if $\mathcal{A}$ is successful in the $\bindattack$ game.

  \[
    \Pr[\bindattack_{\mathcal{A},\Pi}(\kappa) = \true]
    =
    \Pr[\collisionattack_{\mathcal{A}^*,H}(\kappa) = \true]
  \]

  From the collision resistance of $H$ it follows that $\Pr[\collisionattack_{\mathcal{A}^*,H} = \true] < \negl$. Therefore,
  $\Pr[\bindattack_{\mathcal{A},\Pi} = \true] < \negl$, so
  the protocol $\Pi$ is binding.
\end{proof}

We now posit that no adversary can predict the public key of a secure signature scheme, except with negligible probability. We call a distribution \emph{unpredictable} if no
probabilistic polynomial-time adversary can predict its sampling. We give
the formal definition, with some of its statistical properties, in
Appendix~\ref{sec:proofs:unpred-dist}.

\begin{restatable}[Public key unpredictability]{lem}{restateLemPkUnpredictability}
  \label{lem:pk-unpredictability}
  Let $S = (\textsf{Gen}, \textsf{Sig}, \textsf{Ver})$ be a secure signature scheme.
  Then the distribution ensemble
  $X_\kappa = \{(sk, pk) \gets \textsf{Gen}(1^\kappa); pk\}$ is
  unpredictable.
\end{restatable}

The following lemma shows that the output of the random oracle is
indistinguishable from random if the input is unpredictable
(for the complete proofs see Appendix~\ref{sec:proofs:ro}).
For reference, the
definition of computational indistinguishability is included in
Appendix~\ref{sec:proofs:comp-ind}.

\begin{restatable}[Random Oracle unpredictability]{lem}{restateLemRoUnpredictability}
  \label{lem:ro-unpredictability}
  Let $\mathcal{T}$ be an unpredictable distribution ensemble and $H$ be a
  Random Oracle.
  The distribution ensemble $X = \{t \gets \mathcal{T}; H(t)\}$ is indistinguishable from
  the uniform distribution ensemble $\uniform(\{0,1\}^\kappa)$.
\end{restatable}

\begin{theorem}[Uncensorability]
  Let $S = (\Gen, \Sig, \Ver)$ be a \emph{secure signature scheme},
  $H$ be a \emph{Random Oracle},
  and $\mathcal{T}$ be an unpredictable tag distribution.
  Then the protocol of Section~\ref{sec:construction} instantiated with
  $H, S, \mathcal{T}$ is \emph{uncensorable}.
\end{theorem}
\begin{proof}
  Let $X$ be the distribution ensemble of public keys generated using $\GenAddr$
  and $Y$ that of keys generated using $\GenBurnAddr$.

  From Lemma~\ref{lem:pk-unpredictability} the distribution of
  public keys generated from $S$ is unpredictable. The
  function $\GenAddr$ samples a public key from $S$ and applies the
  random oracle $H$ to it. Applying
  Lemma~\ref{lem:ro-unpredictability}, we obtain that
  $X \cind \uniform(\{0, 1\}^\kappa)$.

  The function $H'(x) = H(x) \xor 1$ is a random oracle (despite not
  being independent from the random oracle $H$).
  Since $\mathcal{T}$ is unpredictable, and
  applying Lemma~\ref{lem:ro-unpredictability} with random oracle $H'$, we
  obtain that $Y \cind \uniform(\{0, 1\}^\kappa)$.

  By transitivity, $X$ and $Y$ are computationally indistinguishable.
\end{proof}

From the above, we conclude that the tags used during the burn process must be
unpredictable. If the tag is chosen to contain a randomly generated public key
from a secure signature scheme, or its hash,
Lemmas~\ref{lem:pk-unpredictability}~and~\ref{lem:ro-unpredictability} show that
sufficient entropy exists to ensure uncensorability. Our cross-chain application
makes use of this fact.
