\subsection{Security of Smart Contract Implementation}

\todo{Clean up this section}

We now formalize our protocol and provide a cryptographic analysis of its
security. As NIPoPoWs security is modelled in the Bitcoin
Backbone Protocol~\cite{backbone}, we work in the same model (and note
that the same mathematical model also captures Ethereum). We assume that the
standard results of the backbone protocol are attained, namely blockchain
\emph{persistence} and \emph{liveness}. Persistence and liveness can be proved
to hold with overwhelming probability under the honest mining majority
assumption. For the details of that result, consult the Bitcoin Backbone
paper~\cite{backbone}.

We adopt the sidechains security definition from related work on proof-of-stake
sidechains~\cite{pos-sidechains}.

We will show that proving, to the maintainers of a chain $\mathcal{G}_2$, that
an event $e$ took place in chain $\mathcal{G}_1$ without it actually happening,
can only occur if the underlying NIPoPoWs protocol is insecure. Therefore, our
proof strategy follows the standard form of a cryptographic computational
reduction. In our assumptions, we will make use of the persistence and
liveness of $\mathcal{G}_2$, but only the persistence of $\mathcal{G}_1$.

\begin{theorem}
  Assume a secure NIPoPoWs construction. Then, under the honest majority
  assumption for both $\mathcal{G}_1$ and $\mathcal{G}_2$, for all PPT
  adversaries $\mathcal{A}$ and for all environments $\mathcal{Z}$, the
  proof-of-work sidechains construction between $\mathcal{G}_1$ and
  $\mathcal{G}_2$ with contestation period $2k$ is secure, except with
  negligible probability in $k$.
\end{theorem}
\begin{proof}
  Let $\mathcal{A}$ be an arbitrary PPT adversary against the proof-of-work
  sidechains construction and $\mathcal{Z}$ be an arbitrary environment. We will
  construct an adversary $\mathcal{A}^*$ against NIPoPoWs and an environment
  $\mathcal{Z}^*$ in which it will operate.

  Suppose, without loss of generality, that $\mathcal{A}$ can break the security
  of proof-of-work sidechains during a cross-chain transfer from $\mathcal{G}_1$
  to $\mathcal{G}_2$. (Because the construction is symmetric, if the adversary
  is not able to do that, then they will be able to break the security of a
  cross-chain transfer from $\mathcal{G}_2$ to $\mathcal{G}_1$ and the proof
  follows in the same manner.)

  Note that $\mathcal{A}$ works in an environment with two blockchains,
  $\mathcal{G}_1$ and $\mathcal{G}_2$, while $\mathcal{A}^*$ must work in the
  environment of one blockchain, namely $\mathcal{G}_1$.

  % TODO: Make Z* swallow the environment of Z
  % TODO: Mention that the NIPoPoWs that we use have adaptive predicates
  % LIV_1 -> LIV_2
  $\mathcal{A}^*$ works as follows. First, it simulates the execution of the
  blockchain civilization $\mathcal{G}_2$. That is, it creates a new random
  oracle for $\mathcal{G}_2$ which is independent of its external random oracle
  used with $\mathcal{G}_1$. For any random oracle queries of $\mathcal{A}$
  pertaining to $\mathcal{G}_1$, $\mathcal{A}^*$ forwards the queries to its
  external random oracle. For random oracles queries of $\mathcal{A}$ pertaining
  to $\mathcal{G}_2$, $\mathcal{A}^*$ answers its queries with its simulated
  and independent random oracle. Because $\mathcal{A}$ is subject to honest
  majority limitations in both $\mathcal{G}_1$ and $\mathcal{G}_2$, it follows
  that $\mathcal{A}^*$ will respect honest majority with regards to its external
  random oracle. For any environment instructions requested by $\mathcal{Z}$
  pertaining to $\mathcal{G}_1$ (namely, the creation of new parties), the
  instructions are mirrored by $\mathcal{Z}^*$. Intructions of $\mathcal{Z}$
  pertaining to $\mathcal{G}_2$ are simulated by $\mathcal{A}^*$. All diffusions
  of blocks in $\mathcal{G}_1$ by $\mathcal{A}$ are also diffused by
  $\mathcal{A}^*$, while diffusions in $\mathcal{G}_2$ by $\mathcal{A}$ are held
  private.

  $\mathcal{A}^*$ monitors the chains adopted by honest parties and for every
  round $r$ observes the state of all honest parties. $\mathcal{A}^*$ looks for
  a round $r$, an event $e$, a $\mathcal{G}_1$ maintainer $p_1$ and a
  $\mathcal{G}_2$ maintainer $p_2$ for which the following properties hold:

  \begin{enumerate}
    \item $p_1$ has not included $e$ in their state
    \item $p_2$ has included $e$ in their \textsf{finalized-events} state
  \end{enumerate}

  Because of the construction of $p_2$, \textsf{finalized-events} can contain
  $e$ only if an issuance of \textsf{submit-event-proof} is included at least
  $2k$ blocks deep and contains the respective NIPoPoW $\pi$ stored in
  $\textsf{events}[e].\textsf{proof}$. $\mathcal{A}^*$ now returns the proof
  $\pi$.

  We will now analyze the probability of success of $\mathcal{A}$. Consider
  the following (probabilistic) events:

  \begin{enumerate}
    \item $\textsc{SC-Brk}$ that $\mathcal{A}$ is successful
    \item $\textsc{Cert-Brk}$ that $\mathcal{A}^*$ is successful
    \item $\textsc{Per}_1$ that persistence is maintained in $\mathcal{G}_1$
    \item $\textsc{Per}_2$ that persistence is maintained in $\mathcal{G}_2$
    \item $\textsc{Live}_2$ that liveness is maintained in $\mathcal{G}_2$
    \item $\textsc{BC}$ the union of $\textsc{Per}_1 \land \textsc{Per}_2 \land \textsc{Live}_2$
  \end{enumerate}

  From total probability we obtain:

  \[
  \Pr[\textsc{SC-Brk}] = \Pr[\textsc{SC-Brk}|\textsc{BC}]\Pr[\textsc{BC}]
                       + \Pr[\textsc{SC-Brk}|\lnot \textsc{BC}]\Pr[\lnot \textsc{BC}]
  \]

  From the honest majority assumption of $\mathcal{G}_1$, we deduce that
  $\Pr[\lnot \textsc{Per}_1]$ and $\Pr[\lnot \textsc{Live}_1]$ are negligible,
  and similarly from the honest majority assumption of $\mathcal{G}_2$ we deduce
  that $\Pr[\lnot \textsc{Per}_2]$ is negligible, therefore
  $\Pr[\lnot \textsc{BC}]$ is negligible. It now suffices to show that
  $\Pr[\textsc{SC-Brk}|\textsc{BC}]\Pr[\textsc{BC}]$ is negligible.

  Suppose that $\textsc{SC-Brk}$ occurs. It follows that a (blockchain) event
  $e$ must have been adopted by $p_2$ with some NIPoPoW $\pi$, but not by $p_1$,
  as detailed above. Suppose now that $\textsc{BC}$ occurs.

  Because of the \emph{persistence} of $\mathcal{G}_2$, when $\pi$ was burried
  under $k$ blocks in the adopted chain of $p_2$, all honest parties in
  $\mathcal{G}_2$ must have seen $\pi$ (this warrants the oldest $k$ of the $2k$
  blocks in the contestation period). Because of the \emph{liveness} of
  $\mathcal{G}_2$, at least one honest block must have been included in the last
  $k$ blocks after $\pi$ had been received by all honest parties (this warrants
  the latest $k$ of the $2k$ blocks in the contestation period).

  Because of the \emph{persistence} of $\mathcal{G}_1$, if $e$ is not included
  in the state of $p_1$ at round $r$, then therefore it cannot have been
  included in the state of any $\mathcal{G}_1$ party during round $r - \eta k$.
  It follows that an honest party will attempt and succeed in generating a
  $\mathcal{G}_2$ block containing a contesting proof $\pi^*$ attesting to the
  fraudulence of event $e$ by invoking
  $\textsf{submit-contesting-proof}(\pi^*, e)$ and this block will be adopted by
  $p_2$. As $p_2$ has finalized $e$, then therefore it must be such that
  $\textsf{verify}^{e, \mathcal{G}}_{k,m}(\{\pi, \pi^*\})$, and therefore
  \textsc{Cert-Brk} has occurred.

  Putting the above together, we obtain that:

  \[
  \Pr[\textsc{Cert-Brk}] \geq \Pr[\textsc{SC-Brk}|\textsc{BC}]\Pr[\textsc{BC}]
  \]

  From the NIPoPoW security assumption, we have that $\Pr[\textsc{Cert-Brk}]$ is
  negligible. Therefore, $\Pr[\textsc{SC-Brk}]$ is negligible.
\end{proof}

% TODO: prove correctness, i.e., that an honest user will never be disputed
% successfully by an adversary
