\chapter{Proofs of Proof-of-Stake}\label{chapter:stake}

In this short chapter,
we introduce a novel cryptographic primitive,
\emph{ad-hoc threshold multisignatures (ATMS)},
 fundamental building block for cross-chain certification in proof-of-stake.
We discuss specific instantiations of ATMS in
Section~\ref{sec:auth}.
We implement them in three distinct ways. The first one simply concatenates
signatures of elected slot leaders. While secure, the disadvantage of this
implementation is that the size of the sidechain certificate is $\Theta(k)$
signatures. An improvement can be achieved by employing multisignatures and
Merkle-tree hashing for verification key aggregation;  using this we can drop
the sidechain-certificate size to $\Theta(r)$ signatures where $r$  slot leaders
do not participate in its generation; in the optimistic case $r\ll k$ and thus
this scheme can be a significant improvement in practice. Finally, we show that
STARKs and bulletproofs~\cite{ben2017scalable,bulletproofs} can be used to bring
down the size of the certificate to be optimally succinct in the random oracle
model.  We observe that in the case of an active sidechain (e.g., one that
returns assets at least once per epoch) our construction with succinct sidechain
certificates has optimal storage requirements in the mainchain.

These ATMS will be leveraged in the next chapters to build full sidechains in
the proof-of-stake model.

\input{chapters/stake/tms-definition}
\input{chapters/stake/tms-construction}

% \cite{pos-sidechains}
