\chapter{Introduction}\label{chapter:introduction}

\section{Let there be Bitcoin}
Before money, there was debt~\cite{debt}. Money is a yardstick for measuring
it. Sometimes it takes the form of a gold coin. Not useful in itself, one
accepts it because one assumes other people will. Modern \emph{fiat} money is
not backed by gold, but takes the form of pieces of paper bills or, more often,
bits in the computer systems of banks. Regardless of their manifestation, all
forms of money are debt, which is a social relation~\cite{critical-realism}.

Money functions as a \emph{medium of exchange}, as a \emph{common measure of
value} or \emph{unit of account}, as a \emph{standard of value} or
\emph{standard of deferred payment}, and a \emph{store of
value}~\cite{money-mechanism}. These functions of money rely on the relationship
of the individual with the economic community that accepts money. Each monetary
transaction between two parties is never a ``private matter'' between them,
because it translates to a claim upon society~\cite{philosophy-of-money}.

This gives rise to the need of \emph{consensus}. The economic community must be
able to ascertain, in principle, whether a monetary transaction is \emph{valid}
according to its rules. In a good monetary system, parties of the economic
community must globally agree on the conclusions of such deductions. In simple
words, when someone pays me, I must know that they have sufficient money to do
so, and that this money given to me will be accepted by the economic community
when I later decide to spend it. This judgement of validity consists of two
parts: First, that the money in use has been minted legitimately in the first
place. Secondly, that this money rightfully belongs to the party who is about to
spend it, and has not been spent before, to protect against \emph{double spending}.

The problem of consensus is solved differently in different monetary systems. Gold
coins had stamps whose veracity could be checked, while paper bills have chemical
features making them difficult to duplicate. Such physical features ensure the
legitimacy of minting. The problem of double spending is trivial when it comes to
physical matter: If I give a
gold coin to someone, I no longer hold that gold coin and cannot also give it to
someone else. When coins are digitized, the problem of \emph{who owns what}
is solved by the private bank and payment processors.
A private bank centrally maintains the balance of a bank account to ensure a
corresponding debit card cannot spend more money than it has. In this case, a
vendor's terminal connects to the bank's servers to check the validity of the
payment (and security can only be ensured while the terminal is online). These
cases involve a \emph{trusted third party}\index{Trusted Third Party}, the
bank or the payment processor, to maintain a balance and make a judgement on
whether a transaction is valid. The central bank is relied upon for the
legitimacy of minting. Payment processors and banks who maintain account
balances and make a judgement on whether a transaction is valid are relied upon
to prevent double spending. The economic community depends on these third
parties and trusts them for availability and truthfulness.

The cypherpunk\index{Cypherpunks} political movement and the wave of
cryptographers working on \emph{protocols} in general have an inherent hatred
for trusted third parties. For the former, they amount to
centralization of political power which they wish to see eliminated. For the
latter group, it constitutes a technical challenge -- if the role of the trusted
third party is fully algorithmizable, why not replace the party by a protocol
ran by the economic community themselves? It is somewhere in intersection of the
two that \emph{blockchain} protocols appeared.

Bitcoin\index{Bitcoin} was invented by Satoshi Nakamoto\index{Satoshi Nakamoto}
in 2008. In a paper titled
\emph{A Peer-to-Peer Electronic Cash System}~\cite{bitcoin}, Satoshi introduced
the first \emph{cryptocurrency} and the technology powering it, the
\emph{blockchain}. The paper accompanied an implementation of what has come to
be known as \emph{Bitcoin Core}\index{Bitcoin Core}, the first cryptocurrency
wallet, which was written in C++. Satoshi, whose name was soon deified within
the blockchain community, was nothing but a Japanese pseudonym, the
physical identity and whereabouts of the author or authors still unknown. Never
short on drama, the space was shaken again when Satoshi mysteriously disappeared
without a trace in 2011, leaving the community leaderless, perhaps in an attempt
to, in a sense, remove the last standing trusted third party from the picture.

As an electronic currency, Bitcoin enjoys many advantages. The transmittance of
a transaction takes a couple of seconds, while transactions become secure
against chargebacks in about an hour. It is easy and cheap to move money across
the world in large quantities, with transaction fees remaining constant
regardless of amount moved (at the time of writing, approximately $\$0.05$). The
ecosystem is open, the reference client open source, and the community can
develop their own software to work with it without requesting permission from
anyone.

More interestingly, Bitcoin is the first \emph{decentralized} electronic
currency. Unlike all previous electronic currencies, it does not require any
trusted third party for its operation. There is no company or operator with
privileged access over Bitcoin -- no CEO or corporate network. This makes
the Bitcoin network \emph{sovereign}: It cannot be shut down by a traditional
court of law regardless of the desires of world governments, unless drastic
measures are employed such as shutting down the Internet. There is no central
entity to issue a subpoena to and it will continue to operate as long as it has
are users. This also makes the system uncensorable. Whether this elevated status
is a desirable is disputed~\cite{egalitarianism}.


\section{Motivation}
% superlight clients
% sidechains
\section{Our Contributions}
\section{Related Work}
% KLS
% other sidechains works
% - omniledger
% - rootstock
% - Todd sidechains
% - xclaim
% - rootstock
% - polkadot
% - truebit?
% - flyclient
