\section*{Acknowledgements}
\ifdraft
Acknowledgements to people...
\else
My parents, Efi and Spyros, and my sister Natalia have always inspired me and
been patient and loving. Thank you.

I could not have completed this thesis without the continuous exchange of ideas
with my computer scientist colleagues who read my papers and this thesis and
provided feedback: My co-authors Andrew Miller, Peter Ga\v{z}i, Kostis
Karantias, Orfeas Stefanos Thyfronitis Litos, Dimitris Karakostas, Nikos
Leonardos, Zeta Avarikioti, Roman Brunner, Christos Nasikas,  Alexei Zamyatin,
Roger Wattenhofer, Lefteris Kokoris-Kogias; my University of Athens colleagues,
Katerina Samari, Pyrros Chaidos, Giorgos Panagiotakos; my colleagues Angel Leon,
Sam Patterson, Brian Hoffman, Washington Sanchez; my mentors, Andrew McCann who
taught me how to code, Andreas Moser who taught me to follow my heart, Dimitris
Fotakis who taught me to count, Nikos Papaspyrou who taught me how to think,
Aristidis Arageorgis who taught me how to speak, and Aris Pagourtzis, who
supervised my master thesis; the people whom I've taught and been taught by,
Aleksis Brezas, Petros Angelatos, Themis Papameletiou, Dimitris Lamprinos,
Vitalis Salis, Petros Markopoulos, Eva Sarafianou, Dimitris Grigoriou, Christos
Porios, Andrianna Polydouri, Nikolas Kamarinakis, Giorgos Christoglou, and all
my other teachers and students; and the people who enabled this work but were
not in the spotlight, in particular Tatiana Kyrou and Mirjam Wester.

Last and most importantly, I want to thank my advisor Aggelos Kiayias for
giving me the space and opportunity to learn on my own. But also closely and
patiently mentoring me and teaching me modern cryptography, the importance of
precise definitions, assumptions and proofs, \emph{how to prove and how to
refute}. Above all, for teaching me about the scientific method, the philosophy
of science, the love for what we do, \emph{the moral character of
cryptographic work}, and for helping me navigate the labyrinthian and
always increasing difficulty of completing a thesis. I am greatly
honoured to be his student in the \emph{paradigm shift} he is leading in the
field of blockchain science, political cryptography, and decentralized financial
cryptography.
\fi

I am indebted to IOHK who generously funded my salary and my numerous conference
participations during the years of my PhD. Charles Hoskinson personally ensured
I would never have to worry about funding during my doctoral work. I am also
thankful OB1 and FrostWire for funding my work. Additional funding was provided
by the European Union ERC project CODAMODA as well as H2020 project PRIVILEDGE
\#780477.
